Weather Data Integration and Assimilation System\\

### 2020-02-10 method/sec_3-microservice.tex
Scale cube

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Scale Cube}
\label{subse:scale_cube}
The microservice architecture is an application of Y-axis scaling but let’s also look at X-axis and Z-axis scaling.

\subsubsection{X-axis Saling}
X-axis scaling consists of running multiple copies of an application behind a load balancer. If there are N copies then each copy handles 1/N of the load. This is a simple, commonly used approach of scaling an application.
One drawback of this approach is that because each copy potentially accesses all of the data, caches require more memory to be effective. Another problem with this approach is that it does not tackle the problems of increasing development and application complexity.

\subsubsection{Y-axis Scaling}
Unlike X-axis and Z-axis, which consist of running multiple, identical copies of the application, Y-axis axis scaling splits the application into multiple, different services. Each service is responsible for one or more closely related functions. There are a couple of different ways of decomposing the application into services.
verb-based decomposition ex: checkout
decompose the application by noun ex: customer management. 
An application might use a combination of verb-based and noun-based decomposition.

\subsubsection{Z-axis Scaling}
When using Z-axis scaling each server runs an identical copy of the code (similar to X-axis scaling). The big difference is that each server is responsible for only a subset of the data.

Some component of the system is responsible for routing each request to the appropriate server. Ex;
One commonly used routing criteria is an attribute of the request such as the primary key of the entity being accessed. 
Another common routing criteria is the customer type. For example, an application might provide paying customers with a higher SLA than free customers by routing their requests to a different set of servers with more capacity.

Z-axis splits are commonly used to scale databases. Data is partitioned (a.k.a. sharded) across a set of servers based on an attribute of each record. (Ex: the primary key of the RESTAURANT table is used to partition the rows between two different database servers)

Note that X-axis cloning might be applied to each partition by deploying one or more servers as replicas/slaves. Z-axis scaling can also be applied to applications.
(Example of apply Z-axis scaling: the search service consists of a number of partitions. A router sends each content item to the appropriate partition, where it is indexed and stored. A query aggregator sends each query to all of the partitions, and combines the results from each of them.)

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{The Scale Cube}
\label{subse:scale_cube}
The scalability of a system can explain via a concept called \emph{Scale Cube} which talk about the scalability of the application throw X, Y and Z axis.

\subsubsection{X-axis Saling}
X-axis scaling consists of running multiple copies of an application behind a load balancer. If there are N copies then each copy handles 1/N of the load. This is a simple, commonly used approach of scaling an application TODO.

\subsubsection{Y-axis Scaling}
Unlike X-axis and Z-axis, which consist of running multiple, identical copies of the application, Y-axis axis scaling splits the application into multiple, different services. Each service is responsible for one or more closely related functions. There are a couple of different ways of decomposing the application into services.
\begin{itemize}
    \item verb-based decomposition ex: checkout.
    \item decompose the application by noun ex: customer management. 
    \item An application might use a combination of verb-based and noun-based decomposition.
\end{itemize}

The microservice architecture is an application of Y-axis scaling.

\subsubsection{Z-axis Scaling}
When using Z-axis scaling each server runs an identical copy of the code (similar to X-axis scaling). The big difference is that each server is responsible for only a subset of the data. 
Z-axis splits are commonly used to scale databases. Data is partitioned (a.k.a. sharded) across a set of servers based on an attribute of each record.

Even \acrshort{wdias} is design based on the Y-axis scaling, it's possible to use the Z-axis scaling to scalibility of the system further. This will be more discuss in the section \ref{se:discussion}.
